### 2017-10-02 Risk analysis/Text/Layout/Layout/chapter2_methods.tex
Gradient function to find min/max y X and Y directions

		\section{3D geological reservoir model}
		The concept of the 1D geological model is to be transferred and extended to a 3D setting that incorporates a more complete geological reservoir system. A three-dimensional space allows not only for better consideration of stratigraphical aspects, but also for the inclusion of structural formations, in particular reservoir trap-defining features.\\
		For the purpose of exploring the effect of the methods of Bayesian analysis and decision theory in this work, the model is nevertheless to be kept relatively simple.

		- concept of 1D case in chapter 3 transferred to a 3D case of a structural geological model
		- same again here: relatively simple model including some important typical geological and structural features and giving it an economic meaning
		- alternating layers of sandstones and shales, so typical reservoir and seal formations
		- structurally defined by a tilted dome-formation (folding along in the direction of two perpendicular axes) which is displaced by a standard normal fault
		- these features are arranged in a way, that they result in the formation of a trap, defined by the anticlinal features and the fault, as well as enabled by the presence of a reservoir rock
		- considering a petroleum production industry perspective, actors/ decision makers would be interested in the evaluation of value this potential reservoir
		- "traditionally", this is represented by volumetric calculations or estimations of the recoverable reserves
		- here: maximum volume of entrapment and subsequently, relative or hypothetical volumes of recoverable reserve can be calculated (for each model realization)
		- (later: numbers from example case are taken, to achieve estimations of the NPV for a development project realization)
		- looking at this structural model, not only the calculated volume can be taken into account, but also risk factors, such as fault permeabity seal safety (and capacity?), possible juxtapositions and leaks

@@

		- in the following, the construction and design of this model is described

		- base of the structural geological model is a 3Dcubic  space (block)  with 2000 m size in X, Y and Z x3
		- place layer positional points in three lines, resembling three hypothetical seismic lines as base information
		-

>>>>

		\section{3D geological reservoir model}
		The concept of the 1D geological model is to be transferred and extended to a 3D setting that incorporates a more complete geological reservoir system. A three-dimensional space allows not only for better consideration of stratigraphical aspects, but also for the inclusion of structural formations, in particular reservoir trap-defining features.

		\subsection{Design of the 3D geological reservoir model}\label{sec:3D_design}
		For the purpose of exploring the effect of the methods of Bayesian analysis and decision theory in this work, the model is nevertheless to be kept relatively simple. Stratigraphically, it is designed to include one main reservoir unit (sandstone), one main seal unit (shale), an underlying basement through which hydrocarbon fluids could have flown upwards and an overlying formation that is assumed to be permeable, so that hydrocarbons can leak upwards. Structurally, it is constructed to feature an anticlinal dome fold that is displaced by a normal fault. All layers are tilted so that they dip in the opposite direction of the fault plane dip. The original concept of this model is designed in a way, that a potential hydrocarbon trap is formed in the reservoir rock enclosed by the deformed and tilted seal and normal fault.\\
		This trap is defined as the central feature of economic interest.

		- considering a petroleum production industry perspective, actors/ decision makers would be interested in the evaluation of value this potential reservoir
		- "traditionally", this is represented by volumetric calculations or estimations of the recoverable reserves
		- here: maximum volume of entrapment and subsequently, relative or hypothetical volumes of recoverable reserve can be calculated (for each model realization)
		- (later: numbers from example case are taken, to achieve estimations of the NPV for a development project realization)
		- looking at this structural model, not only the calculated volume can be taken into account, but also risk factors, such as fault permeabity seal safety (and capacity?), possible juxtapositions and leaks

@@

		\subsection{Construction of the 3D geological reservoir model}\label{sec:3D_construction}
		- in the following, the construction and design of this model is described

		- base of the structural geological model is a 3Dcubic  space (block)  with 2000 m size in X, Y and Z x3
		- place layer positional points in three lines, resembling three hypothetical seismic lines as base information

		\subsection{Determination of the trap volume}

			\subsubsection{Finding spill and leak points}

			\subsubsection{Calculating the maximum trap volume}
